### 2013-07-01 latex/SupportingText.tex
Changing Matthew's middle initial.
Updated paper text.

\begin{center}
\Large\textbf{Maximum allowed solvent accessibilites\\of residues in proteins}\\
\large\mbox{}\\
\textbf{Supporting Information}
\end{center}

\bigskip
\noindent Matthew A. Tien, Austin G. Meyer, Dariya K. Sydykova, Stephanie J. Spielman, Claus O. Wilke

@@

\subsection*{Supporting Figures}
\centerline{\includegraphics[width=3.5in]{figures/Alanine_RSA_distribution.pdf}}

\noindent Figure S1. Distribution of RSA values for alanine. RSA was calculated using our theoretically determined normalization values. This distribution is highly non-normal with a strong right skew. Therefore, mean RSA is a poor measure of center for this distribution. Similarly skewed distributions are found for most amino acids.

\newpage
\centerline{\includegraphics[width=6in]{figures/Ala_Rama_HSV_ALL_edited.pdf}}

\noindent Figure S2. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All non-empty bins are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for non-empty bins in (A).

@@

\noindent Figure S3. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All non-empty bins in the GENEROUS regions are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for all bins in the GENEROUS region.

@@

\noindent Figure S4. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All bins in the CORE region are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for all bins in the CORE region.

\newpage
\subsection*{Supporting Tables}

\noindent Table S1. Maximum SA values observed in the empirical and the theoretical data sets.

@@

{\small
\noindent
$^\text{a}$Scale based on mean RSA, as calculated using the theoretially derived SA normalization values. The actual scale is defined as $1-(\text{mean RSA})$, to yield increasingly larger values for more hydrophobic residues.\\
$^\text{b}$Same scale as in (a), but calculated using the empirically derived SA normalization values.\\
$^\text{c}$Fraction of 100\% buried residues, with $\text{RSA}=0$ (corresponding to $\text{SA}<1\text{\AA}$).\\
$^\text{d}$Fraction of 95\% buried residues, with $\text{RSA}<0.05$.
}

>>>>

\begin{center}
\large\textbf{Supporting Information for ``Maximum allowed solvent accessibilites of residues in proteins''}\\
\end{center}

\bigskip
\noindent Matthew Z. Tien, Austin G. Meyer, Dariya K. Sydykova, Stephanie J. Spielman, Claus O. Wilke

@@

\subsection*{Supporting Figures}
\centerline{\includegraphics[width=6in]{figures/Ala_Rama_HSV_ALL_edited.pdf}}

\noindent Figure S1. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All non-empty bins are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for non-empty bins in (A).

@@

\noindent Figure S2. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All non-empty bins in the GENEROUS regions are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for all bins in the GENEROUS region.

@@

\noindent Figure S3. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All bins in the CORE region are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for all bins in the CORE region.

\centerline{\includegraphics[width=3.5in]{figures/Alanine_RSA_distribution.pdf}}

\noindent Figure S4. Distribution of RSA values for alanine. RSA was calculated using our theoretically determined normalization values. This distribution is highly non-normal with a strong right skew. Therefore, mean RSA is a poor measure of center for this distribution. Similarly skewed distributions are found for most amino acids.

\subsection*{Supporting Tables}

\noindent Table S1. Maximum SA values (in \AA$^2$) observed in the empirical and the theoretical data sets.

@@

{\small
\noindent
$^\text{a}$Scale based on mean RSA, as calculated using the theoretially derived SA normalization values for the ALLOWED region. The actual scale is defined as $1-(\text{mean RSA})$, to yield increasingly larger values for more hydrophobic residues.\\
$^\text{b}$Same scale as in (a), but calculated using the empirically derived SA normalization values for the ALLOWED region.\\
$^\text{c}$Fraction of 100\% buried residues, with $\text{RSA}=0$ (corresponding to $\text{SA}<1\text{\AA}$).\\
$^\text{d}$Fraction of 95\% buried residues, with $\text{RSA}<0.05$.
}
